### 2015-01-20 src/discussion.Rnw

\subsubsection{Operator Selection}
From Table~\ref{tbl:selective}, looking at the test and assert utility, we
see that there are a few selective strategies that seem to score a positive
test utility. Notably, the statement modification strategy sselective does
about 1.86\% better than the random selection for test utility, and has
similar advantage in assert utility. It also seem to have a slight advantage
of 0.27\% in the strategy effectivenss.

@@

\subsubsection{Stratified sampling over operators}
For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
baseline. However, we note that the strategy effectiveness is negative. For
t-test, since this is a continuum, we only inspected if the strategy as a
whole (not particular fractions) hold any advantage. The t-test suggests that
there is no significant difference from the baseline for this kind of sampling.

\subsubsection{Stratified sampling over program elements}
For stratified sampling over program elements in Table~\ref{tbl:element},
there appears a small consistent advantage for most sample fractions. The best
utility achieved was 3.85\% for class based $\frac{1}{16}$ sample. As before,
as this is a continuum, we only checked whether this kind of sampling has any
significant advantage as a whole with t-test. The t-test suggests that all
sampling over elements have a small but consistent advantage $p-value < 0.01$

>>>>

\subsection{Operator Selection}
From Table~\ref{tbl:selective}, looking at the test and assert utility, we
see that there are a few selective strategies that seem to score a positive
test utility. Notably, the statement modification strategy sselective does
about 1.86\% better than the random selection for test utility, and has
similar advantage in assert utility. It also seem to have a slight advantage
of 0.27\% in the strategy effectivenss.

@@

\subsection{Stratified sampling over operators}
For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
baseline. However, we note that the strategy effectiveness is negative. For
t-test, since this is a continuum, we only inspected if the strategy as a
whole (not particular fractions) hold any advantage. The t-test suggests that
there is no significant difference from the baseline for this kind of sampling.

\subsection{Stratified sampling over program elements}
For stratified sampling over program elements in Table~\ref{tbl:element},
there appears a small consistent advantage for most sample fractions. The best
utility achieved was 3.85\% for class based $\frac{1}{16}$ sample. As before,
as this is a continuum, we only checked whether this kind of sampling has any
significant advantage as a whole with t-test. The t-test suggests that all
sampling over elements have a small but consistent advantage $p-value < 0.01$
